Hierarchical Time Series Forecasting in Emergency Medical Services

### 2022-11-18 manuscript/title_page.qmd
draft of cover letetr and title page

- **Author contributions:** BRT and RJH conceptualize the the study and designed the experiment. BRT obtained a funding to meet RHH at Monash University. BRT and RJH provided the analysis of the data. RJH developed the models; ML chaired the data oversight committee. BRT drafted the manuscript, and RJH contributed substantially to its revision. BRT takes responsibility for the paper as a whole.

>>>>

- **Author contributions:** BRT and RJH conceptualize the the study and designed the experiment. BRT obtained a funding to meet RJH at Monash University in Melbourne. BRT and RJH provided the analysis of the time series data. RJH developed forecasting models and hierarchical methods; BRT and RJH use R programming to conduct analysis. BRT drafted the manuscript, and RJH contributed substantially to its revision. BRT takes responsibility for the paper as a whole.
